### 2018-03-12 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 translation notes

\end{axis}
\end{tikzpicture}
\end{document}

>>>>

\end{axis}
\end{tikzpicture}
\section{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}
\end{document}
